---
title: "eeg_statistical_analysis"
---
```{r Initialization}
rm(list=ls())

library(yaml)
library(ggplot2)
library(feather)
library(lme4)
library(simr)
library(here)
library(sjPlot)
library(writexl)


# Read the configuration file
config <- yaml.load_file("../config.yml")

eeg_r_dataset_path <- here(config$engagement_index_force_dataset)
df <- read_feather(eeg_r_dataset_path)
df <- na.omit(df)
config$epoch_length

# Convert to factor
df$control_type <- as.factor(df$control_type)
df$hand_type <- as.factor(df$hand_type)
df$subject <- as.factor(df$subject)


#```{r Uncomment these lines to 
#subject_to_leave <- config$subjects[7]
#df <- df[!(df$control_type=="no_force"),]
#df <- df[!(df$subject==subject_to_leave),]

#subject_to_leave <- config$subjects[8]
#df <- df[!(df$control_type=="no_force"),]
#df <- df[!(df$subject==subject_to_leave),]

response <- df$beta_alpha_theta
df['output'] <- response
#write_xlsx(df, 'engagement_index_with_force.xlsx')

df_non <-  df[(df$hand_type=='non_dominant'),]
#{r Plotting}
x <- df$total_force
y <- df$output
# Plot with main and axis titles
# Change point shape (pch = 19) and remove frame.
# Add regression line
plot(x, y, main = "Engagement and Force index",
     xlab = "Force (N)", ylab = "Engagement index",
     pch = 19, frame = FALSE)
abline(lm(y ~ x, data = mtcars), col = "blue")
```


```{r Analysis under non dominant hand with no force as reference}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]
#df_temp <- df
df_non_dominant <-  df_temp[df_temp[, 'hand_type'] == 'non_dominant',]
response <- df_non_dominant$output
df$control_type <- relevel(df$control_type, "no_force")
model3 <- glmer(response ~ control_type + (1 | subject),
               data = df_non_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```


```{r Analysis using both total force and hand type}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]

# Round off the number of significant figures 
df_temp <- df[!(df$control_type=="no_force"),]
df_temp$total_force <- round(df_temp$total_force, digits = 2)
response <- df_temp$output

df_temp$hand_type <- relevel(df_temp$hand_type, "dominant")
model2 <- glmer(response ~ total_force*hand_type + (1 | subject),
               data = df_temp, family = gaussian(link = log))
summary(model2)
tab_model(model2)
```


```{r Analysis using both control type and hand type as factors}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]
#df_temp <- df
response <- df_temp$output

df_temp$control_type <- relevel(df_temp$control_type, "no_force")
df_temp$hand_type <- relevel(df_temp$hand_type, "dominant")
model2 <- glmer(response ~ control_type*hand_type + (1 | subject),
               data = df_temp, family = gaussian(link = log))
summary(model2)
tab_model(model2)
```


```{r Analysis under dominant hand using control type}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]
#df_temp <- df
df_dominant <-  df_temp[df_temp[, 'hand_type'] == 'dominant',]
response <- df_dominant$output
df$control_type <- relevel(df$control_type, "no_force")
model3 <- glmer(response ~ control_type  + (1 | subject),
               data = df_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```


```{r Analysis under non dominant hand using control type}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]

df_non_dominant <-  df_temp[df_temp[, 'hand_type'] == 'non_dominant',]
response <- df_non_dominant$output
df$control_type <- relevel(df$control_type, "no_force")
model3 <- glmer(response ~ control_type + (1 | subject),
               data = df_non_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```

```{r Analysis under non dominant hand using error_reduction as reference}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]

df_non_dominant <-  df_temp[df_temp[, 'hand_type'] == 'non_dominant',]
response <- df_non_dominant$output
df$control_type <- relevel(df$control_type, "error_reduction")
model3 <- glmer(response ~ control_type + (1 | subject),
               data = df_non_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```


```{r Analysis under non dominant hand using total force and dropping no force}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]

df_temp <- df_temp[!(df_temp$control_type=="no_force"),]
df_non_dominant <-  df_temp[df_temp[, 'hand_type'] == 'non_dominant',]
response <- df_non_dominant$output
df$control_type <- relevel(df$control_type, "no_force")
model3 <- glmer(response ~ total_force + (1 | subject),
               data = df_non_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```


```{r Analysis under dominant hand using total force and dropping no force}
subject_to_leave <- config$subjects[8]
df_temp <- df[!(df$subject==subject_to_leave),]

df_temp <- df[!(df$control_type=="no_force"),]
df_non_dominant <-  df_temp[df_temp[, 'hand_type'] == 'dominant',]
response <- df_non_dominant$output
#df$control_type <- relevel(df$control_type, "no_force")
model3 <- glmer(response ~ total_force + (1 | subject),
               data = df_non_dominant, family = gaussian(link = log))
summary(model3)
tab_model(model3)
```

